Análise de Complexidade e Experimental de Algoritmos de Ordenação

### 2018-04-23 Article/article.tex
Primeiro

\hyphenation{op-tical net-works semi-conduc-tor}

@@

>>>>

\usepackage{filecontents,pgfplots}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{filecontents}{pistonkinetics.dat}
n  ale	        cresc       desc
10 0.000364672	0.00036467	0.000729345
100 0.025162379	0.011304841	0.027350422
1000 2.027211827	1.070313195	2.47904228
10000 260.8561041	99.28349187	249.613812
100000 29710.64645	9664.62109818	25154.97916
500000 746315.8556	245270.4554	597291.3591
1000000 3014609.044	967866.5598	2347234.462

\end{filecontents}

\pgfplotstableread{pistonkinetics.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[minor tick num=1,
xlabel=n elementos]
\addplot [black,very thick] table [x={n}, y={ale}] {\pistonkinetics};
\addplot [red,very thick] table [x={n}, y={cresc}] {\pistonkinetics};
\addplot [blue,very thick] table [x={n}, y={desc}] {\pistonkinetics};
\end{axis}
\end{tikzpicture}
\end{document}
